Latitudinal gradients in biotic niche breadth vary across ecosystem types.

### 2016-09-29 manuscript/latitudepaper.tex

\begin{figure}[h]
% \centerline{\includegraphics*[height=.5\textheight]{Figures/Other/conceptual_figure.eps}}
\caption{In A) we show the known scaling relationship between link density (links per species) and 
species richness. This scaling relationship is a power law and therefore linear in a log-log plot.
In B) we show two versions of the latitudinal-niche breadth hypothesis that have been proposed to
explain this gradient. Hypothesis 1 posits that greater environmental stability in the tropics will 
allow species to evolve narrower niches (indicated by parabolas) than those at the poles. Hypothesis 2 
suggests that species will have constant niche sizes over latitude but that greater primary productivity 
in the tropics creates a larger niche space such that each species still occupies a smaller proportion 
of the total niche space. These two hypotheses have different implications for the scaling of food-web 
properties such as the number of feeding links per species with species richness. C) If hypothesis 1 is 
true, then the exponent of the scaling relationship between link density and species richness should 
be larger towards the poles, where each additional species in the food-web will have a larger niche 
(i.e., more feeding links). If hypothesis 2 is true, then the exponent of this distribution should 
not vary significantly over latitude.}
\label{concept}
\end{figure}

\begin{figure}[h]
% \centerline{\includegraphics*[height=.5\textheight]{Figures/by_TL/scaling_with_S/proportions/S_fitlines_nonts.eps}}
\caption{Scaling relationships for re-scaled link density, generality, and vulnerability 
relative to the species richness of a food web. Link density, generality,
and vulnerability were each re-scaled to remove the effects of latitude and ecosystem
type. As these relationships take the form of power laws, we did this by dividing the food-web
property (e.g. link density) by species richness raised to an exponent including the 
effects of latitude and, where applicable, ecosystem type and the interaction between ecosystem
type and latitude. Note that in all cases estuarine food webs were treated as the baseline 
ecosystem type, but that at most two ecosystem types had interactions between ecosystem type and
latitude retained in the best-fit model (see \emph{Results} for specifics). For each relationship, 
we show the re-scaled values (white circles) as well as the overall scaling relationship using estuarine
ecosystems as a baseline (black line, N=196 food webs). For a figure with the uncorrected values,
see Fig.~\emph{S7}, \emph{Appendix S4}.}
\label{props_v_lat}
\end{figure}

\begin{figure}[h]
% \centerline{\includegraphics*[width=.85\textwidth]{Figures/by_TL/marginal/S_marginal_latitude_proportions.eps}}
\caption{Changes to the scaling of link density, generality, and vulnerability with species richness across ecosystem
types and over latitude. We show the estimated scaling exponent for species richness (black
line) with its 95\% confidence interval (in grey), based on N=196 empirical food webs.
Latitude is given in degrees from the equator regardless of direction.} \label{S} \end{figure}

>>>>

\begin{figure}[h]
\centerline{\includegraphics*[height=.5\textheight]{Figures/Other/conceptual_figure.eps}}
\caption{In A) we show the known scaling relationship between link density (links per species) and 
species richness. This scaling relationship is a power law and therefore linear in a log-log plot.
In B) we show two versions of the latitudinal-niche breadth hypothesis that have been proposed to
explain this gradient. Hypothesis 1 posits that greater environmental stability in the tropics will 
allow species to evolve narrower niches (indicated by parabolas) than those at the poles. Hypothesis 2 
suggests that species will have constant niche sizes over latitude but that greater primary productivity 
in the tropics creates a larger niche space such that each species still occupies a smaller proportion 
of the total niche space. These two hypotheses have different implications for the scaling of food-web 
properties such as the number of feeding links per species with species richness. C) If hypothesis 1 is 
true, then the exponent of the scaling relationship between link density and species richness should 
be larger towards the poles, where each additional species in the food-web will have a larger niche 
(i.e., more feeding links). If hypothesis 2 is true, then the exponent of this distribution should 
not vary significantly over latitude.}
\label{concept}
\end{figure}

\begin{figure}[h]
\centerline{\includegraphics*[height=.5\textheight]{Figures/by_TL/scaling_with_S/proportions/S_fitlines_nonts.eps}}
\caption{Scaling relationships for re-scaled link density, generality, and vulnerability 
relative to the species richness of a food web. Link density, generality,
and vulnerability were each re-scaled to remove the effects of latitude and ecosystem
type. As these relationships take the form of power laws, we did this by dividing the food-web
property (e.g. link density) by species richness raised to an exponent including the 
effects of latitude and, where applicable, ecosystem type and the interaction between ecosystem
type and latitude. Note that in all cases estuarine food webs were treated as the baseline 
ecosystem type, but that at most two ecosystem types had interactions between ecosystem type and
latitude retained in the best-fit model (see \emph{Results} for specifics). For each relationship, 
we show the re-scaled values (white circles) as well as the overall scaling relationship using estuarine
ecosystems as a baseline (black line, N=196 food webs). For a figure with the uncorrected values,
see Fig.~\emph{S7}, \emph{Appendix S4}.}
\label{props_v_lat}
\end{figure}

\begin{figure}[h]
\centerline{\includegraphics*[width=.85\textwidth]{Figures/by_TL/marginal/S_marginal_latitude_proportions.eps}}
\caption{Changes to the scaling of link density, generality, and vulnerability with species richness across ecosystem
types and over latitude. We show the estimated scaling exponent for species richness (black
line) with its 95\% confidence interval (in grey), based on N=196 empirical food webs.
Latitude is given in degrees from the equator regardless of direction.} \label{S} \end{figure}
